Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-11 paper/pears.tex
Updates from Overleaf

%%% plots for kinematics
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is XX(XX) kpc, and peaks at $z=0$ with a median separation of XX (xx).
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is XX(XX), to $z=1$, where median separations are XX(XX). The median separation rises more steeply from z=1 to z=0, peaking at $z=0$ with median separations of XX and XX for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.  \todo{fill caption numberss, z=4, replace with 1000 reals plot}
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distirbution tends to spread out more evenly across a large range of separations, thus increasing the median.
  % \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
   \todo{change color of med lines, add z=4, replace with 1000 reals }
    }
  \label{fig:sep-dist}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $xx$ at $z=0$ and $xx$ at $z=4$, and of a massive pair is $xx$ at $z=0$ and $xx$ at $z=4$. 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\kms$ faster than major pairs.  
    \todo{replace with 1000 reals, median "relative" velocity, finish caption, add 0 horizon line}
    }
  \label{fig:vel}
\end{figure*}

>>>>

%%% plots for kinematics
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs closely resembles a power law distribution across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. 
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
  % \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
   \todo{change color of med lines, add z=4, replace with 1000 reals }
    }
  \label{fig:sep-dist}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair). 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
    }
  \label{fig:vel}
\end{figure*}
